Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-07-31 literature/paper_draft.qmd
update sim hierarchical section

- 2x2, 6x6, 50x2

Using the data generating process described above, we consider three different 2-level hierarchical structures, with the bottom-level series $n_b$ being 2 groups of 2 (4 series), 6 groups of 6 (36 series), and 2 groups of 50 (100 series), respectively. The first structure is exactly the same as the one in @fig-hierarchy, with 2 series at the level 1. The second structure has 36 bottom series and are aggregated in groups of size 6 to form 6 level-1 series, which are finally aggregated to form the top level. The third structure is larger, having 100 bottom series aggregated in groups of size 50 to form 2 level-1 series, then aggregated to get the top level. Because of this structure, the VAR(1) coefficients matrix would have entries between groups being zeros. To save space, we will only illustrate the settings of the second structure (6 groups of 6) in @fig-settings-6x6, and the first and third structure is similar.

```{r load results}

sim1_1 <- readRDS("./literature/lib/S4-2-1_T100_M10000_par.rds")
sim1_2 <- readRDS("./literature/lib/S4-2-1_T300_M10000.rds")

sim2_1 <- readRDS("./literature/lib/S36-6-1_T100_M100_run1.rds")
sim2_2 <- readRDS("./literature/lib/S36-6-1_T300_M100_run2.rds")

@@

```{r generate plots for A and Sigma}
# p1_A <- plot_heatmap(sim1_1$A, T) + 
#   ggtitle("2x2 VAR(1) Coefficients Matrix")
# 
# p1_Sigma <- plot_heatmap(cov2cor(sim1_1$Sigma), T) + 
#   ggtitle("2x2 Correlation Matrix")
# 
p2_A <- plot_heatmap(sim2_1$A) +
  ggtitle("VAR(1) Coefficients Matrix") + theme_void()

@@

# p3_A <- plot_heatmap(sim3_1$A) +
#   ggtitle("50x2 VAR(1) Coefficients Matrix")
# 
# p3_Sigma <- plot_heatmap(cov2cor(sim3_1$Sigma), T) +
#   ggtitle("50x2 Correlation Matrix")
```

```{r}
#| out.width: "30%"
#| fig.align: "center"
# (p1_A | p1_Sigma) +
#   plot_layout(guides = "collect") & theme(legend.position = "right")
```

```{r}
#| out.width: "60%"
#| fig.align: "center"
# (p2_A | p2_Sigma) +
#   plot_layout(guides = "collect") & theme(legend.position = "right")
```

```{r}
#| out.width: "100%"
#| fig.align: "center"
# (p3_A | p3_Sigma) +
#   plot_layout(guides = "collect") & theme(legend.position = "right")
```

```{r fig-settings-6x6}
#| label: fig-settings-6x6
#| fig-cap: "Heatmaps of the VAR(1) coefficient matrix and correlation matrix for the 6×6 structure."
#| out.width: "85%"
#| fig.align: "center"

@@

>>>>

Using the data generating process described above, we consider three different 2-level hierarchical structures, with the bottom-level series $n_b$ being 2 groups of 2 (4 series), 6 groups of 6 (36 series), and 2 groups of 50 (100 series), respectively. The first structure is exactly the same as the one in @fig-hierarchy, with 2 series at the level 1. The second structure has 36 bottom series and are aggregated in groups of size 6 to form 6 level-1 series, which are finally aggregated to form the top level. The third structure is larger, having 100 bottom series aggregated in groups of size 50 to form 2 level-1 series, then aggregated to get the top level.

  Because of this structure, the VAR(1) coefficients matrix would have entries between groups being zeros. To save space, we will only illustrate the settings of the second structure (6 groups of 6) in @fig-settings-6x6, and the first and third structure is similar.

```{r load results}
sim1_1 <- readRDS("./literature/lib/S4-2-1_T50_M500.rds")
sim1_2 <- readRDS("./literature/lib/S4-2-1_T300_M500.rds")

sim2_1 <- readRDS("./literature/lib/S36-6-1_T50_M500.rds")
sim2_2 <- readRDS("./literature/lib/S36-6-1_T300_M500.rds")

@@

```{r generate plots for A and Sigma}
p1_A <- plot_heatmap(sim1_1$A, T) + 
  ggtitle("2x2 VAR(1) Coefficients Matrix")

p1_Sigma <- plot_heatmap(cov2cor(sim1_1$Sigma), T) + 
  ggtitle("2x2 Correlation Matrix")

p2_A <- plot_heatmap(sim2_1$A) +
  ggtitle("VAR(1) Coefficients Matrix") + theme_void()

@@

p3_A <- plot_heatmap(sim3_1$A) +
  ggtitle("50x2 VAR(1) Coefficients Matrix")

p3_Sigma <- plot_heatmap(cov2cor(sim3_1$Sigma), T) +
  ggtitle("50x2 Correlation Matrix")
```

```{r fig settings 2x2}
#| label: fig-settings-2x2
#| fig-cap: "Heatmaps of the VAR(1) coefficient matrix and correlation matrix for the 2x2 structure."
#| fig.height: 4
#| fig.width: 6
#| out.width: "55%"
#| fig.align: "center"

p1_A + p1_Sigma + plot_layout(ncol = 2) & theme(legend.position = "bottom")
```

```{r fig settings 6x6}
#| label: fig-settings-6x6
#| fig-cap: "Heatmaps of the VAR(1) coefficient matrix and correlation matrix for the 50x2 structure."
#| fig.height: 4
#| fig.width: 6
#| out.width: "85%"
#| fig.align: "center"

@@

```{r fig settings 50x2}
#| label: fig-settings-50x2
#| fig-cap: "Heatmaps of the VAR(1) coefficient matrix and correlation matrix for the 6×6 structure."
#| fig.height: 12
#| fig.width: 8
#| out.width: "85%"
#| fig.align: "center"

p3_A + p3_Sigma + plot_layout(ncol = 1) & theme(legend.position = "right")
```
